Using Optical Character Recognition in an Applied Research Workflow

### 2020-12-13 outputs/documents/paper.Rmd
Citations update

**[DIEGO - where is this coming from?]** Furthermore, there is a linguistic component that adds more complexity. For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite]**. Not only do these languages have complicated structures and a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji). But often many characters are similar and fonts may have a large effect **[DIEGO - add cite]**. In those cases, the need for reliable approaches to replace an image containing many characters with text of those characters becomes important.

Optical character recognition (OCR) is a process that transforms a image of text into actual text. Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[DIEGO - add cite]**. OCR has been used to parse images of characters since the 1950s, initially using physical processes **[DIEGO - add cite]**. Such approaches were understandably slow and have been replaced by a computer-based recognition system involving the following steps [@Cheriet2007 p. X]:

>>>>

**[The ideas for this paragraph are coming from K.Karthick, K.B.Ravindrakumar, R.Francis, S.Ilankannan = Steps Involved in Text Recognition and Recent Research in OCR. Preprocessing/Factors Affecting the Text Recognition Quality, Chinese Character Recognition, and Arabic Character Recognition as Japanese shared several similarities with Chinese such as Kanji. It is in references folder as F2670037619.pdf]** Furthermore, there is a linguistic component that adds more complexity. For instance, non-Latin characters such as Japanese, Chinese, Arabic, among others, generate several difficulties in different stages of the text mining process **[DIEGO - add cite = same as above]**. Not only do these languages have complicated structures and a large number of categories (for instance, compare the 26 characters in the English alphabet with the thousands of characters in Japanese kanji). But often many characters are similar and fonts may have a large effect **[DIEGO - add cite = same as above]**. In those cases, the need for reliable approaches to replace an image containing many characters with text of those characters becomes important.

Optical character recognition (OCR) is a process that transforms a image of text into actual text. Although there may not be much difference to a human reading a PDF before and after OCR, the main difference is that the PDF is now machine-readable **[This paragraph is comming from Cheriet2007 p. X, Character Recognition Systems: A Guide for Students and Practioners, Chapter 1. It is in references folder as 2007+Character_Recognitio+Pages=[1-4].pdf]**. OCR has been used to parse images of characters since the 1950s, initially using physical processes **[Same as the previous one]**. Such approaches were understandably slow and have been replaced by a computer-based recognition system involving the following steps [@Cheriet2007 p. X]:
